---
title: "variable_investigation"
author: "Steven, Bo, Jiayi"
date: "3/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(ggthemes)
library(hrbrthemes)
```

Dependent Variable: Pixel.Sum, FR_Y, Difference between Res.Freq & Anti.Res.Freq

```{r load data}
data <- read.csv("data/Cleaned_data_03_15.csv")
```

```{r FR_Y vs. Piezo.Batch}
cols <- c("#F76D5E", "#FFFFBF")

data %>% 
    select(FR_Y, Piezo.Batch) %>%
    na.omit() %>% 
    mutate(Piezo.Batch = as.factor(Piezo.Batch)) %>% 
    ggplot(aes(FR_Y, fill = Piezo.Batch, colour = Piezo.Batch, alpha = 0.7)) +
    geom_density() + scale_color_manual(values = cols) +
  labs(title = "ggplot2::theme_minimal", subtitle = "Arial, probably?") +
  theme_minimal()

data %>% 
    select(Pixel.Sum, Piezo.Batch) %>%
    na.omit() %>% 
    mutate(Piezo.Batch = as.factor(Piezo.Batch)) %>% 
    ggplot(aes(Pixel.Sum, fill = Piezo.Batch, colour = Piezo.Batch, alpha = 0.7)) +
    geom_density()

data %>% 
    select(Freq.Diff, Piezo.Batch) %>%
    na.omit() %>% 
    mutate(Piezo.Batch = as.factor(Piezo.Batch)) %>% 
    ggplot(aes(Freq.Diff, fill = Piezo.Batch, colour = Piezo.Batch, alpha = 0.7)) +
    geom_density() + scale_color_fivethirtyeight() +
  theme_fivethirtyeight()
```


```{r FR_Y vs. Row + Column}
p1 <- data %>% 
    select(FR_Y, Row) %>%
    na.omit() %>% 
    mutate(Row = as.factor(Row)) %>% 
    ggplot(aes(FR_Y, Row)) +
    geom_boxplot()

p2 <- data %>% 
    select(FR_Y, Column) %>%
    na.omit() %>% 
    mutate(Column = as.factor(Column)) %>% 
    ggplot(aes(FR_Y, Column)) +
    geom_boxplot()

p3 <- data %>% 
    select(Freq.Diff, Row) %>%
    na.omit() %>% 
    mutate(Row = as.factor(Row)) %>% 
    ggplot(aes(Freq.Diff, Row)) +
    geom_boxplot()

p4 <- data %>% 
    select(Freq.Diff, Column) %>%
    na.omit() %>% 
    mutate(Column = as.factor(Column)) %>% 
    ggplot(aes(Freq.Diff, Column)) +
    geom_boxplot()

p5 <- data %>% 
    select(Pixel.Sum, Row) %>%
    na.omit() %>% 
    mutate(Row = as.factor(Row)) %>% 
    ggplot(aes(Pixel.Sum, Row)) +
    geom_boxplot()

p6 <- data %>% 
    select(Pixel.Sum, Column) %>%
    na.omit() %>% 
    mutate(Column = as.factor(Column)) %>% 
    ggplot(aes(Pixel.Sum, Column)) +
    geom_boxplot()
# need attention, column have values from A-J and 1-10

#grid.arrange(p1, p2, nrow = 1)
p1
p2
p3
p4
p5
p6

res.aov <- aov(Pixel.Sum ~ Column, data = data)
summary(res.aov)
```

The lower and upper hinges correspond to the first and third quartiles. The upper whisker extends from the hinge to the largest value no further than 1.5 * IQR from the hinge. Data plotted individually are outlier points. 
"anova"

```{r Feedrate}
p1 <- data %>% 
    select(FR_Y, Feedrate) %>%
    na.omit() %>% 
    mutate(Feedrate = as.factor(Feedrate)) %>% 
    filter(FR_Y < 10000) %>% # filter out outliers in FR_Y
    ggplot(aes(FR_Y, fill = Feedrate)) +
    geom_density()

p2 <- data %>% 
    select(Freq.Diff, Feedrate) %>% 
    na.omit() %>% 
    mutate(Feedrate = as.factor(Feedrate)) %>% 
    ggplot(aes(Freq.Diff, fill = Feedrate)) + 
    geom_density()

p3 <- data %>% 
    select(Pixel.Sum, Feedrate) %>% 
    na.omit() %>% 
    mutate(Feedrate = as.factor(Feedrate)) %>% 
    ggplot(aes(Pixel.Sum, fill = Feedrate)) + 
    geom_density()
p1
p2
p3
#grid.arrange(p1, p2, p3, nrow = 1)
```
23/110 seems to give better FR_Y value, and not difference between peak separations.

```{r Batch File}
batch_num <- c(readr::parse_number(data$Batch.File)) %>% 
    as.data.frame()
colnames(batch_num) <- c("Batch.Num")
data_batch <- cbind(data, batch_num)

data_batch %>% 
    select(FR_Y, Batch.Num) %>%
    na.omit() %>% 
    ggplot(aes(Batch.Num, FR_Y)) +
    geom_bin_2d(bins = 5) +
    geom_quantile(colour = "orange", size = 2)

data_batch %>% 
    select(Freq.Diff, Batch.Num) %>%
    na.omit() %>% 
    ggplot(aes(Batch.Num, Freq.Diff)) +
    geom_bin_2d(bins = 5) +
    geom_quantile(colour = "orange", size = 2)

data_batch %>% 
    select(Pixel.Sum, Batch.Num) %>%
    na.omit() %>% 
    ggplot(aes(Batch.Num, Pixel.Sum)) +
    geom_bin_2d(bins = 15) +
    geom_quantile(colour = "orange", size = 2)
```

Overtime peak frequency difference did not change much. Pixel Sum and Pixel Sum improved consistantly. 